\documentclass[journal]{IEEEtran}

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage{graphicx}
  \graphicspath{ {./images/} }
  \usepackage{amsmath}
  \usepackage{caption}
  \usepackage{subcaption}
  \usepackage{hyperref}
\else
\fi

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}


\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{DeepProbLog Tasks}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{Davide~Lusuardi,~223821,~\IEEEmembership{davide.lusuardi@studenti.unitn.it}% <-this % stops a space
}

% The paper headers
% \markboth{BIO-INSPIRED ARTIFICIAL INTELLIGENCE, UNITN, JULY~2022}%
% {}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
  DeepProbLog is an extension of ProbLog that integrates Probabilistic Logic Programming with deep learning by means of neural predicates. The neural predicate represents probabilistic facts whose probabilities are parameterized by neural networks.

  DeepProbLog is a framework where general-purpose neural networks and expressive probabilistic-logical modeling and reasoning are integrated in a way that exploits the full expressiveness and strengths of both worlds and can be trained end-to-end based on examples.

  The aim of this report is to show how to solve AI tasks that require the integration of high-level reasoning and low-level perception. We focus on the multi-digit MNIST octal-division task that consists in the division between two lists of MNIST digits representing multi-digit octal numbers. Using DeepProbLog we are able to solve the task given that supervision is only present at the output side of the probabilistic reasoner and considering that the approach can be extended to multi-digit numbers without being explicitly trained on them.  
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
% \begin{IEEEkeywords}
% NEAT, Neural Networks, Neuroevolution, GP, Genetic Algorithm, Artificial Intelligence, Computer Games, Autonomous agent.
% \end{IEEEkeywords}


% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle



\input{01_introduction}
\input{02_task}
\input{03_methodologies_implementation}
\input{04_results}
\input{05_conclusions}


% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{Yellow-Spaceship}
https://github.com/ph3nix-cpu/Yellow-Spaceship

\bibitem{NEAT}
K. O. Stanley and R. Miikkulainen, "Evolving Neural Networks through Augmenting Topologies," in Evolutionary Computation, vol. 10, no. 2, pp. 99-127, June 2002, doi: 10.1162/106365602320169811.

\bibitem{GP}
Koza, John R. "Hierarchical genetic algorithms operating on populations of computer programs." IJCAI. Vol. 89. 1989.

\bibitem{NEAT-Python}
https://neat-python.readthedocs.io/en/latest/index.html

\bibitem{DEAP}
https://deap.readthedocs.io/en/master/index.html

\bibitem{PyGame}
https://www.pygame.org/docs/

\bibitem{repository}
https://github.com/samuelbortolin/Bio-Inspired-Spaceship

\end{thebibliography}

\end{document}


